|

### 2016-05-30 manuscript/thesis_pve.Rmd
added thesis reviewer comment on future experiment only to thesis rmd
tested area based realtionships

##2.4.3 Gas exchange and photosynthetic parameters
At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001). Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively). The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058), but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001). We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`). Across all measurement campaigns and treatments A~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a). A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b). Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001).
\
```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/A_stats_plotting.R")
```  
\
**Figure 2.4**. Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C. Different letters represent significant differences between treatments.

@@

\
Here, reductions in *A~n~* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers. As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers. Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment. Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown. Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers. In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength. Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment.

>>>>

##2.4.3 Gas exchange and photosynthetic parameters
At the first measurement campaign, both A~sat~ and A~max~ were significantly higher in the free seedling treatment compared to seedlings in containers (both P < 0.001). Across all measurement campaigns mean A~sat~ (Figure `r asatfig`) and A~max~ (Table `r pvetab3`) were consistently higher in free seedlings than in containers (26 % and 29 %, respectively). The relationships between photosynthetic capacity, leaf starch and leaf N on a mass basis was marginally significant (P = 0.058), but A~max~ on a mass basis was highly correlated to both leaf N content and leaf starch (both P < 0.001). We used predictions from the linear mixed effect model equation to visualize these relationship of A~max~ to either leaf N content or leaf starch at multiple bin levels (n=5) of the co-variate parameter (Figure `r achemfig`). Across all measurement campaigns and treatments A~max~ was higher when leaf N was also higher, usually associated with low levels of leaf starch (Figure `r achemfig`a). A~max~  was also lower when leaf starch was high as higher leaf N often did not coincide with high leaf starch (Figure `r achemfig`b). These relationships were also analyzed when variables were expressed per unit leaf area and the interpretation of the results did not change, as SLA was similar between treatments. Overall, A~max~ was positively correlated with final harvest biomass across all seedlings (P < 0.001). 
\
```{r asat, fig.width=6, fig.height=6, echo=FALSE,warning=FALSE, message=FALSE, dev="png", dpi=600, dev.args=list(type="cairo")}
source("master_scripts/A_stats_plotting.R")
```  
\
**Figure 2.4**. Soil volume treatment means &pm; standard error, across all measurement campaigns (n = 6), of light saturated rates of photosynthesis at 25 &deg;C. Different letters represent significant differences between treatments.

@@

\
Here, reductions in *A~n~* were positively correlated with decreases in leaf N and leaf N was considerably reduced for seedlings in containers. As leaf N reductions were detected with TNC-free leaf mass, this suggests that physical root restriction or decreased supply likely affected seedling N uptake instead of TNC dilution in leaves in the smallest containers. Root N at the end of the experiment was on average higher in free seedlings but not consistently higher than every container volume treatment. Unrestricted mycorrhizal recruitment could have instead facilitated the increases in leaf N in free seedlings, but this effect is unknown. Combined with the fact that soil N declined evenly across all treatments, there was no clear mechanism present to identify changes in root N uptake between free seedlings and seedlings in containers. In these already low fertility soils, it is possible that seedlings in containers simply grew into increasing N limitation which negatively affected belowground sink strength. Although no clear feedback could be determined between the available soil N pool and decreases in leaf N, the effects of belowground sink limitation on *A~n~* of seedlings in containers was evident throughout the experiment. Future experiments, in which soil N treatments are added, may be able to elucidate the apparent feedbacks between N uptake by roots and leaf N content.
